Usage metrics

### 2020-12-16 analysis/usage.Rmd
Formatting

nb_runs <- E %>%
  pull(file) %>%
  n_distinct()
overview_table(
  r("Corpus",corpus_size),
  r("NbRuns", nb_runs)
) 
```

@@

sites_per_variant <- E %>% # src_ref indicates where the call originates from.
  group_by(ev_variant) %>% 
  summarize( n = n_distinct(src_ref)) # This the number of distinct sites

trig_eval <- sites_per_variant %>% filter(ev_variant == "eval")
trig_eval <- if(nrow(trig_eval) == 0)
{
  0
} else
{
  trig_eval$n
}

trig_evalq <- sites_per_variant %>% filter(ev_variant == "evalq")
trig_evalq <- if(nrow(trig_evalq) == 0)
{
  0
} else
{
  trig_evalq$n
}
trig_eval.parent <- sites_per_variant %>% filter(ev_variant == "eval.parent") 
trig_eval.parent <- if(nrow(trig_eval.parent) == 0)
{
  0
} else
{
  trig_eval.parent$n
}
trig_local <- sites_per_variant %>% filter(ev_variant == "local")
trig_local <- if(nrow(trig_local) == 0)
{
  0
} else
{
  trig_local$n
}

@@

```{r ev-dist, include=FALSE}
eval_calls_table <- E %>% 
  count(ev_package, wt=duplicates, sort = TRUE)
breaks <- c(0, 10^seq(1,8))
group_tags <- cut(eval_calls_table$n,
                  breaks = breaks,
                  include.lowest = TRUE)
ev_summary <- summary(group_tags)

overview_table(
r("bina", ev_summary[[1]]),
r("binb", ev_summary[[2]]),
r("binc", ev_summary[[3]]),
r("bind", ev_summary[[4]]),
r("bine", ev_summary[[5]]),
r("binf", ev_summary[[6]]),
r("bing", ev_summary[[7]]),
r("binh", ev_summary[[8]])) -> TBL
```

>>>>

nb_runs <- E %>%
  pull(file) %>%
  n_distinct()
overview_table(
  r("Corpus", corpus_size),
  r("NbRuns", nb_runs)
)
```

@@

sites_per_variant <- E %>% # src_ref indicates where the call originates from.
  group_by(ev_variant) %>%
  summarize(n = n_distinct(src_ref)) # This the number of distinct sites

trig_eval <- sites_per_variant %>% filter(ev_variant == "eval")
trig_eval <- if (nrow(trig_eval) == 0) {
  0
} else {
  trig_eval$n
}

trig_evalq <- sites_per_variant %>% filter(ev_variant == "evalq")
trig_evalq <- if (nrow(trig_evalq) == 0) {
  0
} else {
  trig_evalq$n
}
trig_eval.parent <- sites_per_variant %>% filter(ev_variant == "eval.parent")
trig_eval.parent <- if (nrow(trig_eval.parent) == 0) {
  0
} else {
  trig_eval.parent$n
}
trig_local <- sites_per_variant %>% filter(ev_variant == "local")
trig_local <- if (nrow(trig_local) == 0) {
  0
} else {
  trig_local$n
}

@@

```{r ev-dist, include=FALSE}
eval_calls_table <- E %>%
  count(ev_package, wt = duplicates, sort = TRUE)
breaks <- c(0, 10^seq(1, 8))
group_tags <- cut(eval_calls_table$n,
  breaks = breaks,
  include.lowest = TRUE
)
ev_summary <- summary(group_tags)

overview_table(
  r("bina", ev_summary[[1]]),
  r("binb", ev_summary[[2]]),
  r("binc", ev_summary[[3]]),
  r("bind", ev_summary[[4]]),
  r("bine", ev_summary[[5]]),
  r("binf", ev_summary[[6]]),
  r("bing", ev_summary[[7]]),
  r("binh", ev_summary[[8]])
) -> TBL
```
